\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-12 paper.qmd
Added hexbin parameter img

The 2D hexagon grid is defined by the number of bins in each direction $(b_1, b_2)$, as given by the centroids of each hexagon $(c_1, c_2)$ and the lower left position where the grid starts at $(s_1, s_2)$, which correspond to the lowest left centroid. The values of $s_i$ need to be below their respective minimum variable values, and could be a full bin lower, to allow a buffer corresponding to a full hexagon width ($a_1$) and height ($a_2$) around the data. The values of $b_i$ are variables to be computed that define the reduction in size of the data ($n$ to $m$).

@@

>>>>

The 2D hexagon grid is defined by the number of bins in each direction $(b_1, b_2)$, as given by the centroids of each hexagon $(c_1, c_2)$ and the lower left position where the grid starts at $(s_1, s_2)$, which correspond to the lowest left centroid. The values of $s_i$ need to be below their respective minimum variable values, and could be a full bin lower, to allow a buffer ($q$) corresponding to a full hexagon width ($a_1$) and height ($a_2$) around the data. The values of $b_i$ are variables to be computed that define the reduction in size of the data ($n$ to $m$).

@@

```{r}
hex_param_vis <- ggplot(data = hex_grid, aes(x = x, y = y)) + 
    geom_polygon(fill = "white", color = "#bdbdbd", aes(group = hex_poly_id)) +
    geom_point(data = all_centroids_df, aes(x = c_x, y = c_y), color = "#31a354") +
    geom_point(data = all_centroids_df |> dplyr::filter(hexID == 1), aes(x = c_x, y = c_y), color = "black") + ## starting point
    geom_rect(aes(xmin = 0, xmax = 1, ymin = 0, ymax = r2), fill = "white", color = "black", alpha = 0, linewidth = 1) +
    geom_segment(x = 0, y = -0.35, xend = 1, yend = -0.35,
                 arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+
    annotate("text", x=0.5, y=-0.45, label= "r1", color = "black") +
    geom_segment(x = -0.25, y = 0, xend = -0.25, yend = r2,
                 arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ 
    annotate("text", x=-0.35, y=1, label= "r2", color = "black") +
    geom_segment(x = -0.1 + 0.2087578, y = -0.15, xend = -0.1 + 0.2087578*2, yend = -0.15,
                   arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ # a1 = 0.2087578
    annotate("text", x=0.2, y=-0.25, label= "a1", color = "black") +
    geom_segment(x = -0.15, y = -0.1*r2 + 0.1807896*2, xend = -0.15, yend = -0.1*r2 + 0.1807896*3,
                     arrow = arrow(length = unit(0.03, "npc"), ends = "both"), color = "black")+ # a2 = 0.1807896
    annotate("text", x=-0.15, y=0.45, label= "a2", color = "black") +
    annotate("text", x=-0.15, y=-0.35, label= "(s1, s2)", color = "black") ## starting point
```

```{r}
#| label: fig-hex-param
#| fig-cap: "Hexagon binning parameters."
#| fig-width: 3
#| fig-height: 3
#| fig-pos: H

hex_param_vis
```

### 2024-05-12 paper.tex
Added hexbin parameter img

The 2D hexagon grid is defined by the number of bins in each direction
\((b_1, b_2)\), as given by the centroids of each hexagon \((c_1, c_2)\)
and the lower left position where the grid starts at \((s_1, s_2)\),
which correspond to the lowest left centroid. The values of \(s_i\) need
to be below their respective minimum variable values, and could be a
full bin lower, to allow a buffer corresponding to a full hexagon width
(\(a_1\)) and height (\(a_2\)) around the data. The values of \(b_i\)
are variables to be computed that define the reduction in size of the
data (\(n\) to \(m\)).

@@

>>>>

The 2D hexagon grid is defined by the number of bins in each direction
\((b_1, b_2)\), as given by the centroids of each hexagon \((c_1, c_2)\)
and the lower left position where the grid starts at \((s_1, s_2)\),
which correspond to the lowest left centroid. The values of \(s_i\) need
to be below their respective minimum variable values, and could be a
full bin lower, to allow a buffer (\(q\)) corresponding to a full
hexagon width (\(a_1\)) and height (\(a_2\)) around the data. The values
of \(b_i\) are variables to be computed that define the reduction in
size of the data (\(n\) to \(m\)).

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-hex-param-1.pdf}

\caption{\label{fig-hex-param}Hexagon binning parameters.}
